Edge sign prediction in general graphs and Correlation Clustering

### 2017-10-23 intro/draft.tex
tiny fixes and ref all over the places

The prevalent setting for most of the works discussed above is that the graph connections are: (i)
homogeneous, in the sense that all edges are of a single type, having the same semantics  between
any pair of nodes; and (ii) based on the \emph{homophily} principle~\autocite{Homophily01}, roughly
meaning that nodes are linked because they are similar. However, many real world situations require
a more complex model, with several kinds of edge and where nodes can be connected if they are
similar only on some dimensions, or even if they are dissimilar. For instance, an e-commerce website
could let its users express whether they find the reviews written by other users helpful or not. As a
more involved example, consider a social network such as Facebook. Whereas the website offers only a
single \emph{friendship} relation, we may want to distinguish between family ties, work ties and
hobbies ties~\autocite{LeskovecEgo12}. Moreover, among one user's \enquote{friends}, there might be some
relations that are actually not positive~\autocite{Yang2012}, whether because of spam, noise or
friendship drift. Note finally that friendship is only one possible kind of relationship between two
users of Facebook, we could also link them whenever they attend the same event or are tagged in the
same post. Yet another possibility would be to study the same set of users across multiple social
networks~\autocite{mergingNetworks16}, in which case the edge type could denote some common
combinations of connections (\eg Twitter+LinkedIn or Facebook+Instagram). In this thesis, we thus
defend the following statement: \textbf{There exists efficient and accurate methods to predict edge
type in complex networks, reyling either only on the graph topology or also on node metadata.}

@@

The first kind of complex networks we consider are \emph{signed graphs}~\autocite{Tang2015a},
where edges carry a positive or a negative sign. Among the many applications of signed graphs, a
natural (and historical~\autocite{harary1953}) one is directed social networks. In such systems,
users can explicitly tag others, stating whether they trust them, support them, like them, or not.
Being able to predict edge signs in such networks improve the user experience, for instance by
promoting courteous online debates~\autocite{journalism15}, assembling efficient teams within
companies~\autocite{MLinHR16} and mitigating cyberbullying~\autocite{cyberbullying13}. Existing
approaches attack the problem along several angles: finding a low dimensional representation of the
nodes based on their connection patterns~\autocites{SIGNet17}{SNE17}, finding a low rank approximation
of the adjacency matrix~\autocites{LowRankCompletion14}{OnlineCompletion17} or extracting
topological features and training classifiers~\autocites{Leskovec2010}{Bayesian15}{wu2016troll}.
Guided by the idea that every user exhibit trollness to various extent, we propose a simple sign
generative model. This model naturally leads to two batch algorithms, one that probably approximate the
Bayes optimal predictor when the training set is dense enough, and one that approximate the maximum
likelihood estimates through label propagation. Extensive experiments on synthetic and real datasets
show that in addition to their sound theoretical foundations, our methods are competitive with the
state of the art in predictive performance, while being more scalable. To illustrate this point, a
short extract of our results is presented in \autoref{tab:troll}.

\begin{table}[ptbh]
  \centering
  \caption{Matthews Correlation Coefficient measuring binary prediction performance (the closer to
    100 the better) in a \aut{}
    network as the proportion of labeled training edges grows. The best result is in red, the
  second one in blue, and our two methods are highlighted in gray.\label{tab:troll}}
  \vspace{0.5\baselineskip}
  \begin{tabular}{lccccc|r}
    \toprule
    method           & 5\%               & 10\%              & 15\%              & 20\%              & 25\%              & time (ms)            \\
    \midrule
    \uslogregp{}     & 19.8              & 27.9              & \vsecondSig{33.2} & 36.9              & 39.7              & \np{4}               \\
    \rowcolor{gray!20!white}
    \usrule{}        & \vsecondSig{19.8} & \vsecondSig{28.0} & 33.1              & \vsecondSig{37.1} & 39.7              & \textbf{\textless 1} \\
    \rowcolor{gray!20!white}
    \uslpropGsec{}   & \vfirstSig{24.2}  & \vfirstSig{31.7}  & \vfirstSig{36.1}  & \vfirstSig{38.9}  & \vfirstSig{41.1}  & \textbf{\np{19}}     \\
    \midrule
    \autocite{LowRankCompletion14}   & 12.4              & 17.9              & 22.0              & 25.7              & 29.0              & \np{3222}            \\
    \autocite{OnlineCompletion17}   & 1.2               & 12.6              & 22.2              & 30.3              & 36.5              & \np{23229}           \\
    \autocite{Leskovec2010}    & 11.4              & 17.2              & 21.0              & 24.3              & 27.0              & \textbf{\np{7}}      \\
    \autocite{wu2016troll} & 17.5              & 25.1              & 31.2              & 35.2              & 37.8              & \np{157}             \\
    \autocite{Bayesian15}  & 15.2              & 25.5              & 32.0              & 36.7              & \vsecondSig{39.8} & \np{4787}            \\
    \bottomrule
  \end{tabular}
\end{table}

@@

In all these cases, graphs are not directed and nodes are not human beings, meaning we can hardly
assign them trollness.  Therefore, we make a different assumption, positing that nodes are
partitioned in $K$ groups in such a way that links within groups are positive and links across
groups are negative. Recovering the optimal partition from the observation of all the edge signs is
called \pcc{}~\autocite{Bansal2002} in the Machine Learning field. Whereas it has been proved to be
\NPc{} to even approximate in the worst case~\autocites{Charikar2003}{Demaine2006}, our thorough
literature review paints a less gloomy landscape. Not only does there exist
exact~\autocite{Berg2015} and fixed-parameters tractable algorithms~\autocites{GoldenCE12}{Fomin2014},
efficient approximation~\autocites{CCPivotConf05}{ChawlaArxiv14} and large scale
heuristics~\autocites{Levorato2015}{Facchetti2011isingmodel}{Kappes2016}, but beyond the worst case,
we are interested in instances that exhibit stability under
perturbation~\autocites{clusteringFeasibility15}{StableCC09}{StableLP09} or are obtained through
random moves from an ideal case~\autocites{plantedAilon09}{Makarychev2014}. This leads us to develop
a spanning tree tailored to predicting edge signs in an active setting~\autocite{Cesa-Bianchi2012b},
where the learner is allowed to select its training labels in the most informative way. The idea is
to ensure that for every edge we will predict, there will be a path in the tree as short as
possible~\autocites{LowerBound95}{Abraham2012} from which we have queried all the signs. We call
this structure \gtx{}, as it recursively build stars of stars. 
We present preliminary results showing that on certain
kind of graphs, this indeed results in better predictive performance than a competitive baseline.
Namely, we create synthetic graphs of growing size with the \lpa{} model~\autocite{Barabasi1999},
partition the nodes in two clusters, set the edge signs accordingly and finally flip a fraction of
the signs \uar{}. As showed on \autoref{fig:gtx_xp_pasynthmcc}, \gtx{} always predict signs better than a
\bfs{} tree rooted at the highest degree node, especially when the noise level is low. Furthermore,
\gtx{} is less sensible to the graph size.

\begin{figure}[phtb]
  \centering
  \includegraphics[width=.8\textwidth]{gtx_exp/pasynthmcc}
  \caption{The Matthews Correlation Coefficient of \bfs{} and \gtx{} on synthetic \lpa{} graphs as a
    function of the number of nodes and of the fraction of signs who have been flipped from the
    hidden two-clustering.  \label{fig:gtx_xp_pasynthmcc}}
\end{figure}

@@

Our approach is to seek a small number of vectors that, once assigned to every edge, best explain
the graph (\ie maximize a score function between the vector assigned to an edge  and the profiles of
this edge's endpoints).
From this initial formulation, we derive two optimization problems, and initially solve them on
synthetic data, generated with a few natural topological constraints. We compared these solutions
with the result of a baseline approach that simply clusters the pairwise profile vectors using
$k$-means. As showed on \autoref{fig:edge}, on a graph with \np{500} nodes, \np{1300} edges and 7
types of edges (where each node is involved in at most 3 types of relation), we recover the hidden
edge assignment more accurately than the $k$-means baseline.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{assets/raw/Gfixed_over0_step2_7dirs3_ambi.pdf}
  \caption{Distribution of the Adjusted Mutual Information (the closer to $1$ the better) over
  \np{600} generations of 7 random directions, comparing our \textsf{optim} method with the $k$-means
baseline. \label{fig:edge}}
\end{figure}

>>>>

The prevalent setting for most of the works discussed above is that the graph connections are: (i)
homogeneous, in the sense that all edges are of a single type, having the same semantics  between
any pair of nodes; and (ii) based on the \emph{homophily} principle~\autocite{Homophily01}, roughly
meaning that nodes are linked because they are similar. However, many real world situations require
a more complex model, with several kinds of edge and where nodes can be connected if they are
similar only on some dimensions, or even if they are dissimilar. For instance, an e-commerce website
could let its users express whether they find the reviews written by other users helpful or not. As a
more involved example, consider a social network such as Facebook. Whereas the website offers only a
single \emph{friendship} relation, we may want to distinguish between family ties, work ties and
hobbies ties~\autocite{LeskovecEgo12}. Moreover, among one user's \enquote{friends}, there might be some
relations that are actually not positive~\autocite{Yang2012}, whether because of spam, noise or
friendship drift. Note finally that friendship is only one possible kind of relationship between two
users of Facebook, we could also link them whenever they attend the same event or are tagged in the
same post. Yet another possibility would be to study the same set of users across multiple social
networks~\autocite{mergingNetworks16}, in which case the edge type could denote some common
combinations of connections (\eg Twitter+LinkedIn or Facebook+Instagram). In this thesis, we thus
defend the following statement: \textbf{There exists efficient and accurate methods to predict edge
type in complex networks, relying either only on the graph topology or also on node metadata.}

@@

The first kind of complex networks we consider are \emph{signed graphs}~\autocite{Tang2015a},
where edges carry a positive or a negative sign. Among the many applications of signed graphs, a
natural (and historical~\autocite{harary1953}) one is directed social networks. In such systems,
users can explicitly tag others, stating whether they trust them, support them, like them, or not.
Being able to predict edge signs in such networks improve the user experience, for instance by
promoting courteous online debates~\autocite{journalism15}, assembling efficient teams within
companies~\autocite{MLinHR16} and mitigating cyberbullying~\autocite{cyberbullying13}. Existing
approaches attack the problem along several angles: finding a low dimensional representation of the
nodes based on their connection patterns~\autocites{SIGNet17}{SNE17}, finding a low rank approximation
of the adjacency matrix~\autocites{LowRankCompletion14}{OnlineCompletion17} or extracting
topological features and training classifiers~\autocites{Leskovec2010}{Bayesian15}{wu2016troll}.
Guided by the idea that every user exhibit trollness to various extent, we propose a simple sign
generative model. This model naturally leads to two batch algorithms, one that probably approximate the
Bayes optimal predictor when the training set is dense enough, and one that approximate the maximum
likelihood estimates through label propagation. Extensive experiments on synthetic and real datasets
show that in addition to their sound theoretical foundations, our methods are competitive with the
state of the art in predictive performance, while being more scalable.
\iffalse
To illustrate this point, a
short extract of our results is presented in \autoref{tab:troll}.

\begin{table}[ptbh]
  \centering
  \caption{Matthews Correlation Coefficient measuring binary prediction performance (the closer to
    100 the better) in a \aut{}
    network as the proportion of labeled training edges grows. The best result is in red, the
  second one in blue, and our two methods are highlighted in gray.\label{tab:troll}}
  \vspace{0.5\baselineskip}
  \begin{tabular}{lccccc|r}
    \toprule
    method           & 5\%               & 10\%              & 15\%              & 20\%              & 25\%              & time (ms)            \\
    \midrule
    \uslogregp{}     & 19.8              & 27.9              & \vsecondSig{33.2} & 36.9              & 39.7              & \np{4}               \\
    \rowcolor{gray!20!white}
    \usrule{}        & \vsecondSig{19.8} & \vsecondSig{28.0} & 33.1              & \vsecondSig{37.1} & 39.7              & \textbf{\textless 1} \\
    \rowcolor{gray!20!white}
    \uslpropGsec{}   & \vfirstSig{24.2}  & \vfirstSig{31.7}  & \vfirstSig{36.1}  & \vfirstSig{38.9}  & \vfirstSig{41.1}  & \textbf{\np{19}}     \\
    \midrule
    \autocite{LowRankCompletion14}   & 12.4              & 17.9              & 22.0              & 25.7              & 29.0              & \np{3222}            \\
    \autocite{OnlineCompletion17}   & 1.2               & 12.6              & 22.2              & 30.3              & 36.5              & \np{23229}           \\
    \autocite{Leskovec2010}    & 11.4              & 17.2              & 21.0              & 24.3              & 27.0              & \textbf{\np{7}}      \\
    \autocite{wu2016troll} & 17.5              & 25.1              & 31.2              & 35.2              & 37.8              & \np{157}             \\
    \autocite{Bayesian15}  & 15.2              & 25.5              & 32.0              & 36.7              & \vsecondSig{39.8} & \np{4787}            \\
    \bottomrule
  \end{tabular}
\end{table}
\fi

@@

In all these cases, graphs are not directed and nodes are not human beings, meaning we can hardly
assign them trollness.  Therefore, we make a different assumption, positing that nodes are
partitioned in $K$ groups in such a way that links within groups are positive and links across
groups are negative. Recovering the optimal partition from the observation of all the edge signs is
called \pcc{}~\autocite{Bansal2002} in the Machine Learning field. Whereas it has been proved to be
\NPc{} to even approximate in the worst case~\autocites{Charikar2003}{Demaine2006}, our thorough
literature review paints a less gloomy landscape. Not only does there exist
exact~\autocite{Berg2015} and fixed-parameters tractable algorithms~\autocites{GoldenCE12}{Fomin2014},
efficient approximation~\autocites{CCPivotConf05}{ChawlaArxiv14} and large scale
heuristics~\autocites{Levorato2015}{Facchetti2011isingmodel}{Kappes2016}, but beyond the worst case,
we are interested in instances that exhibit stability under
perturbation~\autocites{clusteringFeasibility15}{StableCC09}{StableLP09} or are obtained through
random moves from an ideal case~\autocites{plantedAilon09}{Makarychev2014}. This leads us to develop
a spanning tree tailored to predicting edge signs in an active setting~\autocite{Cesa-Bianchi2012b},
where the learner is allowed to select its training labels in the most informative way. The idea is
to ensure that for every edge we will predict, there will be a path in the tree as short as
possible~\autocites{LowerBound95}{Abraham2012} from which we have queried all the signs. We call
this structure \gtx{}, as it recursively build stars of stars. 
\iffalse
We present preliminary results showing that on certain
kind of graphs, this indeed results in better predictive performance than a competitive baseline.
Namely, we create synthetic graphs of growing size with the \lpa{} model~\autocite{Barabasi1999},
partition the nodes in two clusters, set the edge signs accordingly and finally flip a fraction of
the signs \uar{}. As showed on \autoref{fig:gtx_xp_pasynthmcc}, \gtx{} always predict signs better than a
\bfs{} tree rooted at the highest degree node, especially when the noise level is low. Furthermore,
\gtx{} is less sensible to the graph size.

\begin{figure}[phtb]
  \centering
  \includegraphics[width=.8\textwidth]{gtx_exp/pasynthmcc}
  \caption{The Matthews Correlation Coefficient of \bfs{} and \gtx{} on synthetic \lpa{} graphs as a
    function of the number of nodes and of the fraction of signs who have been flipped from the
    hidden two-clustering.  \label{fig:gtx_xp_pasynthmcc}}
\end{figure}
\fi

@@

Our approach is to seek a small number of vectors that, once assigned to every edge, best explain
the graph (\ie maximize a score function between the vector assigned to an edge  and the profiles of
this edge's endpoints).
\iffalse
From this initial formulation, we derive two optimization problems, and initially solve them on
synthetic data, generated with a few natural topological constraints. We compared these solutions
with the result of a baseline approach that simply clusters the pairwise profile vectors using
$k$-means. As showed on \autoref{fig:edge}, on a graph with \np{500} nodes, \np{1300} edges and 7
types of edges (where each node is involved in at most 3 types of relation), we recover the hidden
edge assignment more accurately than the $k$-means baseline.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{assets/raw/Gfixed_over0_step2_7dirs3_ambi.pdf}
  \caption{Distribution of the Adjusted Mutual Information (the closer to $1$ the better) over
  \np{600} generations of 7 random directions, comparing our \textsf{optim} method with the $k$-means
baseline. \label{fig:edge}}
\end{figure}
\fi

### 2017-10-23 packages.tex
add new dataset, competitor and results
mark content added from the aistats paper
minor corrections in troll experiments and add missing figures
write about a possible connection between signed graphs and vector graphs
add some refs
tiny fixes and ref all over the places

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{csquotes}
\usepackage{babel}
\usepackage[heightrounded]{geometry}
\usepackage{setspace}
\usepackage{xspace}
\usepackage{microtype}
\usepackage[citestyle=alphabetic, bibstyle=ieee-alphabetic, isbn=false, maxnames=1, minnames=1,
sorting=nyvt, backref=true, backend=biber, defernumbers=true,maxbibnames=60]{biblatex}
\renewcommand*{\bibfont}{\normalfont\footnotesize}
\AtEveryBibitem{
   % \clearfield{arxivId}
   % \clearfield{booktitle}
   % \clearfield{doi}
   % \clearfield{eprint}
   % \clearfield{eventdate}
   \clearfield{isbn}
   \clearfield{issn}
   % \clearfield{journaltitle}
   \clearfield{month}
   % \clearfield{number}
   % \clearfield{pages}
   \clearfield{series}
   \clearfield{url}
   \clearfield{urldate}
   \clearfield{venue}
   % \clearfield{volume}
   % \clearlist{location} % alias to field 'address'
   \clearlist{publisher}
   \clearname{editor}
}
\addbibresource{/home/orphee/data/projects/biblio/library.bib}
\addbibresource{more.bib}
\addbibresource{gtx.bib}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{import}
\usepackage{mathtools}
\usepackage{sidenotes}
\let\bottomfootnote\footnote
\renewcommand{\footnote}[1]{\sidenote{\footnotesize #1}}
\usepackage[shortlabels]{enumitem}
\usepackage{tabulary}
\usepackage{bm}
\usepackage{multirow}
\usepackage[marginpar]{todo}
\usepackage[np,autolanguage]{numprint}
\usepackage{listings}
\lstset{frame=none, language=Python, tabsize=4,}
% \usepackage{inconsolata}
\usepackage{nicefrac}
\input{drawing}

@@

\usepackage{mdframed}
\newenvironment{aside}%
{\begin{mdframed}[hidealllines=true, leftline=true, innertopmargin=0.5ex, innerbottommargin=0.5ex,
      innermargin=2.3em, leftmargin=2.3em, outermargin=0em, innerleftmargin=0.7em, innerrightmargin=0pt,
      linewidth=1.5pt, skipabove=\baselineskip, skipbelow=\baselineskip,
   linecolor=DodgerBlue!30!White]\small}%
{\end{mdframed}}
\usepackage{stmaryrd}

\usepackage{varioref}
\usepackage{hyperref}
\hypersetup{%
    % draft,    % = no hyperlinking at all (useful in b/w printouts)
    colorlinks=true, linktocpage=true, pdfstartpage=3, pdfstartview=FitV,%
    % uncomment the following line if you want to have black links (e.g., for printing)
    %colorlinks=false, linktocpage=false, pdfborder={0 0 0}, pdfstartpage=3, pdfstartview=FitV,%
    breaklinks=true, pdfpagemode=UseNone, pageanchor=true, pdfpagemode=UseOutlines,%
    plainpages=false, bookmarksnumbered, bookmarksopen=true, bookmarksopenlevel=1,%
    hypertexnames=true, pdfhighlight=/O,%nesting=true,%frenchlinks,%
    urlcolor=Chocolate, linkcolor=RoyalBlue, citecolor=LimeGreen, %pagecolor=RoyalBlue,%
}
\newcommand{\marginpars}[1]{\marginpar{\small#1}}
\usepackage{caption}
\usepackage[margin=0pt,font+=small,labelformat=parens,labelsep=space,
skip=6pt,list=false,hypcap=false]{subcaption}
\captionsetup{compatibility=false}
\usepackage{graphicx}
\usepackage{booktabs}
\graphicspath{{./assets/}}
% \usepackage[capitalize,noabbrev]{cleveref}
\usepackage[]{extdash}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{csquotes}
\usepackage{babel}
\usepackage[heightrounded]{geometry}
\usepackage{setspace}
\usepackage{xspace}
\usepackage{microtype}
\usepackage[citestyle=alphabetic, bibstyle=ieee-alphabetic, isbn=false, maxnames=1, minnames=1,
sorting=nyvt, backref=true, backend=biber, defernumbers=true,maxbibnames=60]{biblatex}
\renewcommand*{\bibfont}{\normalfont\footnotesize}
\AtEveryBibitem{
   % \clearfield{arxivId}
   % \clearfield{booktitle}
   % \clearfield{doi}
   % \clearfield{eprint}
   % \clearfield{eventdate}
   \clearfield{isbn}
   \clearfield{issn}
   % \clearfield{journaltitle}
   \clearfield{month}
   % \clearfield{number}
   % \clearfield{pages}
   \clearfield{series}
   \clearfield{url}
   \clearfield{urldate}
   \clearfield{venue}
   % \clearfield{volume}
   % \clearlist{location} % alias to field 'address'
   \clearlist{publisher}
   \clearname{editor}
}
\addbibresource{/home/orphee/data/projects/biblio/library.bib}
\addbibresource{more.bib}
\addbibresource{gtx.bib}
\addbibresource{rapport.bib}
\addbibresource{/home/orphee/data/projects/magnet/work/edge-vector-label/gsc.bib}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
% \usepackage{bbm}
% \usepackage{bbold}
\usepackage{bm}
% \usepackage{dsfont}
\usepackage{import}
\usepackage{mathtools}
\usepackage{sidenotes}
\let\bottomfootnote\footnote
% \renewcommand{\footnote}[1]{\sidenote{\footnotesize #1}}
\usepackage[shortlabels]{enumitem}
\usepackage{tabulary}
\usepackage{multirow}
\usepackage[marginpar]{todo}
\usepackage[np,autolanguage]{numprint}
\usepackage{listings}
\lstset{frame=none, language=Python, tabsize=4,}
% \usepackage{inconsolata}
\usepackage{nicefrac}
\input{drawing}

@@

\usepackage{mdframed}
\usepackage[breakable]{tcolorbox}
\newenvironment{aside}%
{\begin{mdframed}[hidealllines=true, leftline=true, innertopmargin=0.5ex, innerbottommargin=0.5ex,
      innermargin=2.3em, leftmargin=2.3em, outermargin=0em, innerleftmargin=0.7em, innerrightmargin=0pt,
      linewidth=1.5pt, skipabove=\baselineskip, skipbelow=\baselineskip,
   linecolor=DodgerBlue!30!White]\small}%
{\end{mdframed}}
% \newenvironment{newcontent}%
% {\begin{mdframed}[hidealllines=true, leftline=true, rightline=true, innertopmargin=0.3ex,
%       innerbottommargin=0.3ex,
%       innermargin=-.75em, leftmargin=-.75em,
%       outermargin=-.75em, rightmargin=-.75em,
%       innerleftmargin=0.75em, innerrightmargin=0.75em,
%       linewidth=1.3pt, skipabove=0,
%       skipbelow=0, linecolor=Black!20!White]}%
% {\end{mdframed}}
\usepackage{stmaryrd}

\usepackage{varioref}
\usepackage{hyperref}
\hypersetup{%
    % draft,    % = no hyperlinking at all (useful in b/w printouts)
    colorlinks=true, linktocpage=true, pdfstartpage=3, pdfstartview=FitV,%
    % uncomment the following line if you want to have black links (e.g., for printing)
    %colorlinks=false, linktocpage=false, pdfborder={0 0 0}, pdfstartpage=3, pdfstartview=FitV,%
    breaklinks=true, pdfpagemode=UseNone, pageanchor=true, pdfpagemode=UseOutlines,%
    plainpages=false, bookmarksnumbered, bookmarksopen=true, bookmarksopenlevel=1,%
    hypertexnames=true, pdfhighlight=/O,%nesting=true,%frenchlinks,%
    urlcolor=Chocolate, linkcolor=RoyalBlue, citecolor=LimeGreen, %pagecolor=RoyalBlue,%
}
\newcommand{\marginpars}[1]{\marginpar{\small#1}}
\usepackage{caption}
\usepackage[margin=0pt,labelformat=parens,labelsep=space,%font+=small,
skip=6pt,list=false,hypcap=false]{subcaption}
\captionsetup{compatibility=false}
\captionsetup[subfigure]{labelformat=parens,labelsep=space}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{makecell}
\renewcommand\theadfont{\small}
\graphicspath{{./assets/}}
% \usepackage[capitalize,noabbrev]{cleveref}
\usepackage[]{extdash}
\usepackage[]{calc}
\newlength{\fullpage}
